### 2022-10-10 proposal/Proposal.tex
Update Proposal.tex

\documentclass[12pt]{article}

\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}

\usepackage{lipsum}
\usepackage[colorlinks=true, citecolor=blue]{hyperref}

%% meta data

\title{Proposal: Association between Breast Cancer and Hepatitis C Virus}
\author{Amy Traianou\\
  Department of Statistics\\
  University of Connecticut
}

\begin{document}
\maketitle

\paragraph{Introduction}
For this paper I decided to explore the risk factors associated with breast cancer in women. 
\citep{dwivedi2017analysis}

\paragraph{Specific Aims}
Specifically, I want to determine if there is an association between testing positive for hepatitis C virus
and breast cancer. Both Hepatitis C and breast cancer are extremely prevalent in Egypt \citep{Hussein2021high}. 
Very recently on October 6th, Egypt and Qatar agreed to collaborate in the health sector and use each 
other's expertise. The health ministers specifically mentioned research in Hepatitis C and breast cancer
as a area of interest \citep{arham2022egypt}. Thus, research surrounding these diseases is becoming more
important in the field.

\paragraph{Data}
The data I will be using is from a retrospective study conducted in 2020 \citep{2020association}. The data includes 405 subjects as
part of the study group, all having been treated for breast cancer in the past 10 years. The second group consists of 145 adult females
from a governorate in Egypt, who all participated in a cross-sectional study from 2015-2017.

\paragraph{Research Design and Methods}
To test the association of breast cancer and Hepatitis C, I am going to use Fisher's Exact test.

\paragraph{Discussion}
I expect to find an association.

\paragraph{Conclusion}
This is the conclusion.

\bibliography{../manuscript/refs}
\bibliographystyle{chicago}

\end{document}

### 2022-10-10 proposal/Proposal.tex
Added table

@@
 \usepackage{natbib}
+\usepackage{array}
 
@@
 \paragraph{Introduction}
-For this paper I decided to explore the risk factors associated with breast cancer in women. 
-\citep{dwivedi2017analysis}
+For this paper I decided to explore the risk factors associated with breast cancer in women. Breast cancer is extremely
+prevalent and researchers are constantly trying to determine risk factors to identify women for preventative exams.
+There are many studies attempting to determine if there is an association between certain risk factors and 
+breast cancer including chronic hepatitis C infection \citep{Larrey2010is} and hepatitis B \citep{vishnu2016does}.
 
@@
 \paragraph{Data}
-The data I will be using is from a retrospective study conducted in 2020 \citep{2020association}. The data includes 405 subjects as
+The data I will be using is from a retrospective case control study conducted in 2020 \citep{2020association}. The data includes 405 subjects as
 part of the study group, all having been treated for breast cancer in the past 10 years. The second group consists of 145 adult females
-from a governorate in Egypt, who all participated in a cross-sectional study from 2015-2017.
+from a governorate in Egypt, who all participated in a cross-sectional study from 2015-2017. This data can be put into a 2x2 contingency table
+for statistical analysis.
+
+\begin{tabular}{ | m{1m} | m{1cm}| m{1cm} | m{1cm} | }
+  \hline
+  Risk Factor  & Study Group & Control & Total\\ 
+  \hline
+  Anti-HCV Seropositive & 88 & 15 & 103 \\ 
+  \hline
+  Anti-HCV Seronegative & 317 & 130 & 447 \\ 
+  \hline
+  Total & 405 & 145 & 550 \\ 
+  \hline
+\end{tabular}
 
 \paragraph{Research Design and Methods}
-To test the association of breast cancer and Hepatitis C, I am going to use Fisher's Exact test.
+To test the association of breast cancer and Hepatitis C, I am going to use either the chi-square or Fisher's Exact test, depending on the
+conditions from the sample size \citep{warner2013testing}. Fisher's exact test is useful for when the normality assumption is violated 
+and the expected values of the 2x2 table are too small. The test uses the hypergeometric distribution to test if the probabilities are
+the same between the two groups. Thus, we can determine if there is more of a risk of breast cancer for those with seropositive Hep C. As
+ a result, we can determine if women who chronically test positive should be tested more frequently because they are at a higher risk.
 
 \paragraph{Discussion}
-I expect to find an association.
+I expect to find an association between hepatitis C and breast cancer because there is some existing research that agrees with the association.
+Therefore, this paper would corroborate the exisitng assumptions while giving them more of a basis. Although the potential impacts are quite 
+minimal, the more research that supports the association, the better. If the investigation is not what I expect, then I would suggest more
+data needs to be collected surrounding women with breast cancer in Eygpt. Specifically, a full prospective study with new samples.
 
 \paragraph{Conclusion}
-This is the conclusion.
+In conclusion, I propose using data from women in Egypt to determine if there is an association between seropositive Hepatitis C and 
+breast cancer. The Egyptian government has identified breast cancer as an area of interest for medical research so it has importance in
+the field. Additionally, identifying a new risk factor for breast cancer would increase preventative screening in adult women and hopefully 
+improve the ability to discover cancer in earlier stages.
 

### 2022-10-10 proposal/Proposal.tex
added fig
added titlepage

@@
-\documentclass[12pt]{article}
+\documentclass[12pt, titlepage]{article}
 
@@
 \paragraph{Introduction}
+
 For this paper I decided to explore the risk factors associated with breast cancer in women. Breast cancer is extremely
@@
 \paragraph{Data}
+
 The data I will be using is from a retrospective case control study conducted in 2020 \citep{2020association}. The data includes 405 subjects as
@@
 
-\begin{tabular}{ | m{1m} | m{1cm}| m{1cm} | m{1cm} | }
+\begin{tabular}{ | m{5cm} | m{3cm}| m{3cm} | m{2cm} | }
   \hline
@@
 \paragraph{Research Design and Methods}
+
 To test the association of breast cancer and Hepatitis C, I am going to use either the chi-square or Fisher's Exact test, depending on the
@@
 
+Figure~\ref{fig:formula} shows the probability of the original table occuring.
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=8cm]{formula.png}
+  \caption{This is the hypergeometric pmf.}
+  \label{fig:formula}
+\end{figure}
+
 \paragraph{Discussion}
+
 I expect to find an association between hepatitis C and breast cancer because there is some existing research that agrees with the association.
@@
 \paragraph{Conclusion}
+
 In conclusion, I propose using data from women in Egypt to determine if there is an association between seropositive Hepatitis C and 
@@
 
-\bibliography{../manuscript/refs}
+\bibliography{.../manuscript/refs.bibliography}
 \bibliographystyle{chicago}

### 2022-11-13 manuscript/manuscript.tex
Create manuscript.tex

--- 2022-10-10 proposal/Proposal.tex
@@
 
-%% meta data
-
 \title{Proposal: Association between Breast Cancer and Hepatitis C Virus}
@@
 
+\doublespace
+
+\begin{abstract}
+The Kolmogorov--Smirnov (KS) test is one of the most popular goodness-of-fit
+tests for comparing a sample with a hypothesized continuous distribution.
+Nevertheless, it has often been misused. The standard one-sample KS test applies
+to independent, continuous data with a hypothesized distribution that is
+completely specified. It is not uncommon, however, to see in the literature that
+it was applied to dependent, discrete, or rounded data, with hypothesized
+distributions containing estimated parameters. For example, it has been
+``discovered'' multiple times that the test is too conservative when
+hypothesized distribution has parameters that need to be estimated.
+We demonstrate misuses of the one-sample KS test in
+three scenarios through simulation studies:
+1) the hypothesized distribution has unspecified parameters;
+2) the data are serially dependent; and
+3) a combination of the first two scenarios.
+For each scenario, we provide remedies for practical applications.
+
+\bigskip
+\noindent{\sc Keywords}:
+nonparametric bootstrap;
+parametric bootstrap.
+\end{abstract}
+
 \paragraph{Introduction}
-
+\label{sec:intro}
 For this paper I decided to explore the risk factors associated with breast cancer in women. Breast cancer is extremely
@@
 
-\paragraph{Specific Aims}
 Specifically, I want to determine if there is an association between testing positive for hepatitis C virus
@@
 \paragraph{Data}
-
+\label{sec:data}
 The data I will be using is from a retrospective case control study conducted in 2020 \citep{2020association}. The data includes 405 subjects as
@@
 for statistical analysis.
+
+\vspace{1cm}
 
@@
 
-\paragraph{Research Design and Methods}
-
+\paragraph{Methods}
+\label{sec:methods}
 To test the association of breast cancer and Hepatitis C, I am going to use either the chi-square or Fisher's Exact test, depending on the
@@
 
-\paragraph{Discussion}
-
+\paragraph{Application}
+\label{sec:app}
 I expect to find an association between hepatitis C and breast cancer because there is some existing research that agrees with the association.
@@
 
-\paragraph{Conclusion}
+\paragraph{Discussion}
+\label{sec:discuss}
+I expect to find an association between hepatitis C and breast cancer because there is some existing research that agrees with the association.
+Therefore, this paper would corroborate the exisitng assumptions while giving them more of a basis. Although the potential impacts are quite 
+minimal, the more research that supports the association, the better. If the investigation is not what I expect, then I would suggest more
+data needs to be collected surrounding women with breast cancer in Eygpt. Specifically, a full prospective study with new samples.
 
-In conclusion, I propose using data from women in Egypt to determine if there is an association between seropositive Hepatitis C and 
-breast cancer. The Egyptian government has identified breast cancer as an area of interest for medical research so it has importance in
-the field. Additionally, identifying a new risk factor for breast cancer would increase preventative screening in adult women and hopefully 
-improve the ability to discover cancer in earlier stages.
-
-\bibliography{.../manuscript/refs.bibliography}
+\bibliography{../manuscript/refs}
 \bibliographystyle{chicago}

### 2022-11-14 manuscript/manuscript.tex
Update manuscript.tex
update

--- 2022-10-10 proposal/Proposal.tex
@@
 
-%% meta data
-
-\title{Proposal: Association between Breast Cancer and Hepatitis C Virus}
+\title{Association between Breast Cancer and Hepatitis C Virus with Age Confounding}
 \author{Amy Traianou\\
@@
 
-\paragraph{Introduction}
+\begin{abstract}
+The Kolmogorov--Smirnov (KS) test is one of the most popular goodness-of-fit
+tests for comparing a sample with a hypothesized continuous distribution.
+Nevertheless, it has often been misused.
+
+\bigskip
+\noindent{\sc Keywords}:
+Breslow-Day;
+Fisher's Exact Test;
+Mantel-Haenszel.
+\end{abstract}
+
+\section{Introduction}
+\label{sec:intro}
 
@@
 
-\paragraph{Data}
+\section{Data}
+\label{sec:data}
 
-The data I will be using is from a retrospective case control study conducted in 2020 \citep{2020association}. The data includes 405 subjects as
-part of the study group, all having been treated for breast cancer in the past 10 years. The second group consists of 145 adult females
-from a governorate in Egypt, who all participated in a cross-sectional study from 2015-2017. This data can be put into a 2x2 contingency table
+The data I will be using is from a retrospective case control study conducted in 2020 \citep{2020association}. 
+The data includes 405 subjects as part of the study group, all having been treated for breast cancer in the 
+past 10 years. The second group consists of 145 adult females from a governorate in Egypt, who all participated 
+in a cross-sectional study from 2015-2017. This data can be put into a 2x2 contingency table
 for statistical analysis.
 
-\begin{tabular}{ | m{5cm} | m{3cm}| m{3cm} | m{2cm} | }
+\vspace{1cm}
+
+2x2 Contingency Table for all patients.
+
+\begin{tabular}{ | m{4cm} | m{4cm}| m{4cm} | m{2cm} | }
+  \label{table:total}
   \hline
-  Risk Factor & Study Group & Control & Total\\ 
+    & HCV Seropositive & HCV Seronegative & Total\\ 
   \hline
-  Anti-HCV Seropositive & 88 & 15 & 103 \\ 
+  Breast Cancer & 88 & 317 & 405 \\ 
   \hline
-  Anti-HCV Seronegative & 317 & 130 & 447 \\ 
+  No Cancer Diagnosis & 15 & 130 & 145 \\ 
   \hline
-  Total & 405 & 145 & 550 \\ 
+  Total & 103 & 447 & 550 \\ 
   \hline
@@
 
-\paragraph{Research Design and Methods}
+\vspace{1cm}
+
+2x2 Contingency Table for pateints younger than 45.
+
+\begin{tabular}{ | m{4cm} | m{4cm}| m{4cm} | m{2cm} | }
+  \label{table:young}
+  \hline
+    & HCV Seropositive & HCV Seronegative & Total\\ 
+  \hline
+  Breast Cancer & 17 & 110 & 127 \\ 
+  \hline
+  No Cancer Diagnosis & 2 & 91 & 93 \\ 
+  \hline
+  Total & 19 & 201 & 220 \\ 
+  \hline
+\end{tabular}
+
+\vspace{1cm}
+
+2x2 Contingency Table for patients older than 45.
+
+\begin{tabular}{ | m{4cm} | m{4cm}| m{4cm} | m{2cm} | }
+  \label{table:old}
+  \hline
+    & HCV Seropositive & HCV Seronegative & Total\\ 
+  \hline
+  Breast Cancer & 71 & 207 & 278 \\ 
+  \hline
+  No Cancer Diagnosis & 13 & 39 & 52 \\ 
+  \hline
+  Total & 84 & 246 & 330 \\ 
+  \hline
+\end{tabular}
+
+\section{Methods}
+\label{sec:methods}
 
@@
   \includegraphics[width=8cm]{formula.png}
-  \caption{This is the hypergeometric pmf.}
+  \caption{Hypergeometric pmf.}
   \label{fig:formula}
@@
 
-\paragraph{Discussion}
+\section{Application}
+\label{sec:app}
 
@@
 
-\paragraph{Conclusion}
+\section{Discussion}
+\label{sec:discuss}
 
-In conclusion, I propose using data from women in Egypt to determine if there is an association between seropositive Hepatitis C and 
-breast cancer. The Egyptian government has identified breast cancer as an area of interest for medical research so it has importance in
-the field. Additionally, identifying a new risk factor for breast cancer would increase preventative screening in adult women and hopefully 
-improve the ability to discover cancer in earlier stages.
+I expect to find an association between hepatitis C and breast cancer because there is some existing research that agrees with the association.
+Therefore, this paper would corroborate the exisitng assumptions while giving them more of a basis. Although the potential impacts are quite 
+minimal, the more research that supports the association, the better. If the investigation is not what I expect, then I would suggest more
+data needs to be collected surrounding women with breast cancer in Eygpt. Specifically, a full prospective study with new samples.
 
-\bibliography{.../manuscript/refs.bibliography}
+\bibliography{../manuscript/refs}
 \bibliographystyle{chicago}

### 2022-11-14 manuscript/manuscript.tex
update
intro

@@
 
-\title{Association between Breast Cancer and Hepatitis C Virus with Age Confounding}
+\title{Association between Breast Cancer and Hepatitis C Virus with Age Controlling}
 \author{Amy Traianou\\
@@
 
-For this paper I decided to explore the risk factors associated with breast cancer in women. Breast cancer is extremely
+This paper will explore the risk factors associated with breast cancer in women. Breast cancer is extremely
 prevalent and researchers are constantly trying to determine risk factors to identify women for preventative exams.
@@
 
-Specifically, I want to determine if there is an association between testing positive for hepatitis C virus
-and breast cancer. Both Hepatitis C and breast cancer are extremely prevalent in Egypt \citep{Hussein2021high}. 
-Very recently on October 6th, Egypt and Qatar agreed to collaborate in the health sector and use each 
+Specifically, this paper will determine if there is an association between testing positive for hepatitis C virus
+and breast cancer while controlling for age. Both Hepatitis C and breast cancer are extremely prevalent in 
+Egypt \citep{Hussein2021high}. Very recently on October 6th, Egypt and Qatar agreed to collaborate in the 
+health sector and use each 
 other's expertise. The health ministers specifically mentioned research in Hepatitis C and breast cancer
@@
 
+The rest of the paper is organized into several sections. Section~\ref{sec:data}
+describes the study done in 2020 to test if HCV seropositivity is associated with 
+breast cancer diagnosis in Egyptian population. Section~\ref{sec:methods} 
+describes the following statistical methods; Fisher's Exact Test, Breslow-Day test,
+and Mantel-Haenszel method.
+Section~\ref{sec:app} applies the methods to data from the study, including
+stratafied between ages.
+Section~\ref{sec:discuss} concludes the paper.
+
 \section{Data}
@@
 
-The data I will be using is from a retrospective case control study conducted in 2020 \citep{2020association}. 
-The data includes 405 subjects as part of the study group, all having been treated for breast cancer in the 
-past 10 years. The second group consists of 145 adult females from a governorate in Egypt, who all participated 
-in a cross-sectional study from 2015-2017. This data can be put into a 2x2 contingency table
+The data used in the paper is from a retrospective case control study 
+conducted in 2020 \citep{2020association}. The data includes 405 subjects 
+as part of the study group, all having been treated for breast cancer in the 
+past 10 years. The second group consists of 145 adult females from a 
+governorate in Egypt, who all participated in a cross-sectional study 
+from 2015-2017. This data can be put into a 2x2 contingency table
 for statistical analysis.
+
+\section{Methods}
+\label{sec:methods}
+
+To test the association of breast cancer and Hepatitis C, one can use
+the chi-square or Fisher's Exact test, depending on the
+conditions from the sample size \citep{warner2013testing}. Fisher's
+exact test is useful for when the normality assumption is violated 
+and the expected values of the 2x2 table are too small. The test uses 
+the hypergeometric distribution to test if the probabilities are
+the same between the two groups. Thus, we can determine if there is 
+more of a risk of breast cancer for those with seropositive Hep C. As
+ a result, we can determine if women who chronically test positive should 
+ be tested more frequently because they are at a higher risk.
+
+Figure~\ref{fig:formula} shows the probability of the original table occuring.
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=8cm]{formula.png}
+  \caption{Hypergeometric pmf.}
+  \label{fig:formula}
+\end{figure}
+
+\section{Application}
+\label{sec:app}
 
@@
 
-2x2 Contingency Table for all patients.
+2x2 Contingency Table for all patients:
 
 \begin{tabular}{ | m{4cm} | m{4cm}| m{4cm} | m{2cm} | }
-  \label{table:total}
   \hline
@@
 
-2x2 Contingency Table for pateints younger than 45.
+2x2 Contingency Table for pateints younger than 45:
 
 \begin{tabular}{ | m{4cm} | m{4cm}| m{4cm} | m{2cm} | }
-  \label{table:young}
   \hline
@@
 
-2x2 Contingency Table for patients older than 45.
+2x2 Contingency Table for patients older than 45:
 
 \begin{tabular}{ | m{4cm} | m{4cm}| m{4cm} | m{2cm} | }
-  \label{table:old}
   \hline
@@
 
-\section{Methods}
-\label{sec:methods}
-
-To test the association of breast cancer and Hepatitis C, I am going to use either the chi-square or Fisher's Exact test, depending on the
-conditions from the sample size \citep{warner2013testing}. Fisher's exact test is useful for when the normality assumption is violated 
-and the expected values of the 2x2 table are too small. The test uses the hypergeometric distribution to test if the probabilities are
-the same between the two groups. Thus, we can determine if there is more of a risk of breast cancer for those with seropositive Hep C. As
- a result, we can determine if women who chronically test positive should be tested more frequently because they are at a higher risk.
-
-Figure~\ref{fig:formula} shows the probability of the original table occuring.
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=8cm]{formula.png}
-  \caption{Hypergeometric pmf.}
-  \label{fig:formula}
-\end{figure}
-
-\section{Application}
-\label{sec:app}
-
-I expect to find an association between hepatitis C and breast cancer because there is some existing research that agrees with the association.
-Therefore, this paper would corroborate the exisitng assumptions while giving them more of a basis. Although the potential impacts are quite 
-minimal, the more research that supports the association, the better. If the investigation is not what I expect, then I would suggest more
-data needs to be collected surrounding women with breast cancer in Eygpt. Specifically, a full prospective study with new samples.
-
 \section{Discussion}
@@
 
-I expect to find an association between hepatitis C and breast cancer because there is some existing research that agrees with the association.
-Therefore, this paper would corroborate the exisitng assumptions while giving them more of a basis. Although the potential impacts are quite 
-minimal, the more research that supports the association, the better. If the investigation is not what I expect, then I would suggest more
-data needs to be collected surrounding women with breast cancer in Eygpt. Specifically, a full prospective study with new samples.
+-
 

### 2022-11-14 manuscript/manuscript.tex
equations

@@
 \begin{abstract}
-The Kolmogorov--Smirnov (KS) test is one of the most popular goodness-of-fit
-tests for comparing a sample with a hypothesized continuous distribution.
-Nevertheless, it has often been misused.
+In Egypt Hepatitus C virus infection is a common problem that often impedes treatment
+of Breast Cancer in female patients. While previous work has analyze an associaiton 
+between HCV seropositivity and breast cancer diagnosis, this paper will focus on the 
+potential confounding of age on the association. We will use Fisher's Exact Test to
+estimate the crude estimate of the association and the Mantel-Haenszel method to 
+stratify the data between ages. The possible effect of age in the association can
+lead to improved care for patients.
 
@@
 Specifically, this paper will determine if there is an association between testing positive for hepatitis C virus
-and breast cancer while controlling for age. Both Hepatitis C and breast cancer are extremely prevalent in 
-Egypt \citep{Hussein2021high}. Very recently on October 6th, Egypt and Qatar agreed to collaborate in the 
-health sector and use each 
+and breast cancer while controlling for age in Egyptian populations. Both Hepatitis C and breast 
+cancer are extremely prevalent in Egypt \citep{Hussein2021high}. Very recently on October 6th, 
+Egypt and Qatar agreed to collaborate in the health sector and use each 
 other's expertise. The health ministers specifically mentioned research in Hepatitis C and breast cancer
@@
 
-The data used in the paper is from a retrospective case control study 
-conducted in 2020 \citep{2020association}. The data includes 405 subjects 
-as part of the study group, all having been treated for breast cancer in the 
-past 10 years. The second group consists of 145 adult females from a 
-governorate in Egypt, who all participated in a cross-sectional study 
-from 2015-2017. This data can be put into a 2x2 contingency table
-for statistical analysis.
+The data used in this paper is from a 2020 retrospective case-control 
+study based on Egyptian female populations \citep{2020association},
+sponsered by Mansoura University in Egypt.
 
-\section{Methods}
-\label{sec:methods}
+The study group consists of 405 patients treated at the Oncology Center 
+- Mansoura University in the past 10 years. In order to be included, 
+invasive breast cancer must be biopsy-proven. Patients with unknown 
+viral marker status, multiple cancer diagnoses and virus-unrelated 
+hepatic pathology were all excluded.
 
-To test the association of breast cancer and Hepatitis C, one can use
-the chi-square or Fisher's Exact test, depending on the
-conditions from the sample size \citep{warner2013testing}. Fisher's
-exact test is useful for when the normality assumption is violated 
-and the expected values of the 2x2 table are too small. The test uses 
-the hypergeometric distribution to test if the probabilities are
-the same between the two groups. Thus, we can determine if there is 
-more of a risk of breast cancer for those with seropositive Hep C. As
- a result, we can determine if women who chronically test positive should 
- be tested more frequently because they are at a higher risk.
-
-Figure~\ref{fig:formula} shows the probability of the original table occuring.
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=8cm]{formula.png}
-  \caption{Hypergeometric pmf.}
-  \label{fig:formula}
-\end{figure}
-
-\section{Application}
-\label{sec:app}
+The control group consists of 
+data from a previous study, conducted from 2015-2017. There are 145 
+females from the same geographic distribution, all with no previous 
+cancer diagnosis. In both groups, all patients are above the age of 
+18. For this paper, patients are stratified based on age- older patients 
+are considered 45 years or above and younger patients are below 45 years. 
+The data is summarized in the following 2x2 contingency tables.
 
@@
   \hline
-    & HCV Seropositive & HCV Seronegative & Total\\ 
+    & Breast Cancer & No Cancer Diagnosis & Total\\ 
   \hline
-  Breast Cancer & 88 & 317 & 405 \\ 
+  HCV Seropositive & 88 & 15 & 103 \\ 
   \hline
-  No Cancer Diagnosis & 15 & 130 & 145 \\ 
+  HCV Seronegative & 317 & 130 & 447 \\ 
   \hline
-  Total & 103 & 447 & 550 \\ 
+  Total & 405 & 145 & 550 \\ 
   \hline
@@
   \hline
-    & HCV Seropositive & HCV Seronegative & Total\\ 
+    & Breast Cancer & No Cancer Diagnosis & Total\\ 
   \hline
-  Breast Cancer & 17 & 110 & 127 \\ 
+  HCV Seropositive & 17 & 2 & 19 \\ 
   \hline
-  No Cancer Diagnosis & 2 & 91 & 93 \\ 
+  HCV Seronegative & 110 & 91 & 201 \\ 
   \hline
-  Total & 19 & 201 & 220 \\ 
+  Total & 127 & 93 & 220 \\ 
   \hline
@@
   \hline
-    & HCV Seropositive & HCV Seronegative & Total\\ 
+    & Breast Cancer & No Cancer Diagnosos & Total\\ 
   \hline
-  Breast Cancer & 71 & 207 & 278 \\ 
+  HCV Seropositive & 71 & 13 & 84 \\ 
   \hline
-  No Cancer Diagnosis & 13 & 39 & 52 \\ 
+  HCV Seronegative & 207 & 39 & 246 \\ 
   \hline
-  Total & 84 & 246 & 330 \\ 
+  Total & 278 & 52 & 330 \\ 
   \hline
 \end{tabular}
+
+\section{Methods}
+\label{sec:methods}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=8cm]{table.png}
+  \caption{2x2 Contingency Table}
+  \label{fig:table}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=8cm]{formula.png}
+  \caption{Hypergeometric pmf}
+  \label{fig:formula}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=12cm]{2x2 stratified table.png}
+  \caption{2x2 Contingency Table with Stratified Data}
+  \label{fig:strat}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=8cm]{breslow day test stat.png}
+  \caption{Breslow Day Test Statistic}
+  \label{fig:BD}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=8cm]{MH Test Stat.png}
+  \caption{Mantel-Haenszel Test Statistic}
+  \label{fig:MH}
+\end{figure}
+
+To test the association of breast cancer and Hepatitis C seropositivity, one can use
+the chi-square or Fisher's Exact test, depending on the
+conditions from the sample size \citep{warner2013testing}. Fisher's
+exact test is useful for when the normality assumption is violated 
+and the expected values of the 2x2 table are too small. The test uses 
+the hypergeometric distribution to test if the probabilities are
+the same between the two groups. Thus, we can determine if there is 
+more of a risk of breast cancer for those with seropositive Hep C.
+In the data section, the data was summarized into 2x2 contingency tables.
+The generalzied table is shown in Figure~\ref{fig:table}.
+The first step is calculate the probability of the original table occuring,
+using the hypergeometric pdf. Figure~\ref{fig:formula} shows the formula used.
+
+Based on the alternative hypothesis, you then calculate the probability of 
+all more extreme tables based on the a value. In this paper, p1 is the
+probability of having breast cancer given that the patient is seropositive
+and p2 is the probability of having breat cancer given that the patient
+is seronegative. Then, we want to determine if there is an association,
+specifically if the risk of having breast cancer is higher for those who
+are seropositive. The alternative hypothesis is that p1 is greater than p2-
+which will be tested in the application section.
+
+After calculating the crude estimate, a Breslow-Day test will test for 
+homogeneity of odds ratios between the age stratified data. The generalized
+form of stratified 2x2 contingency tables is shown in Figure~\ref{fig:strat}.
+The Breslow-Day test statistic is shown in Figure~\ref{fig:BD}, which will
+be computed using SAS.
+
+Based on the results of the Breslow Day test for homogeneity of odds ratios,
+the Mantel-Haenszel test will compute a common odds ratio and test if there 
+is an association between seropositivity and breast cancer while controlling 
+for age. The Mantel-Haenszel test statistic is shown in Figure~\ref{fig:MH}
+where the expected value of A is 
+\begin{equation}
+  E(A_{i})=\frac{M_{i1}R_{1i}}{N_{i}} 
+\end{equation}
+and the variance of A is 
+\begin{equation}
+  V(A_{i})=\frac{R_{1i}R_{0i}M_{1i}M_{0i}}{N_i^2(N_{i}-1)}. 
+\end{equation}
+
+\section{Application}
+\label{sec:app}
+-
 

### 2022-11-14 manuscript/manuscript.tex
intro

@@
 
-This paper will explore the risk factors associated with breast cancer in women. Breast cancer is extremely
-prevalent and researchers are constantly trying to determine risk factors to identify women for preventative exams.
-There are many studies attempting to determine if there is an association between certain risk factors and 
-breast cancer including chronic hepatitis C infection \citep{Larrey2010is} and hepatitis B \citep{vishnu2016does}.
+This paper will explore the risk factors associated with breast 
+cancer in women. Breast cancer is extremely prevalent and researchers 
+are constantly trying to determine risk factors to identify women for preventative exams.
+There are many studies attempting to determine if there is an association 
+between certain risk factors and breast cancer including chronic hepatitis 
+C infection \citep{Larrey2010is} and hepatitis B \citep{vishnu2016does}.
 
-Specifically, this paper will determine if there is an association between testing positive for hepatitis C virus
-and breast cancer while controlling for age in Egyptian populations. Both Hepatitis C and breast 
-cancer are extremely prevalent in Egypt \citep{Hussein2021high}. Very recently on October 6th, 
-Egypt and Qatar agreed to collaborate in the health sector and use each 
-other's expertise. The health ministers specifically mentioned research in Hepatitis C and breast cancer
-as a area of interest \citep{arham2022egypt}. Thus, research surrounding these diseases is becoming more
-important in the field.
+Specifically, this paper will examine if there is an association between 
+testing positive for hepatitis C virus and breast cancer while controlling 
+for age in Egyptian populations. Both Hepatitis C and breast 
+cancer are extremely prevalent in Egypt \citep{Hussein2021high}.
+Additionally, research has found that women who are seropositive for 
+HCV have more agressive forms of breast cancer. However, there is 
+minimal research concerning the effect of age on the associaiton.
+
+Recently on October 6th, Egypt and Qatar agreed to collaborate in the health sector and use each 
+other's expertise. The health ministers specifically mentioned research 
+in Hepatitis C and breast cancer as an area of interest \citep{arham2022egypt}. 
+This meeting emphasizes the importance of diving into Hepatitus C Virus 
+and it's association with breast cancer. There have been conflicting
+foundings so studies should indenify additional variables that could 
+contribute to better understanding the relationship. For that reason,
+this paper is focusing on controlling for age of female patients.
 
@@
 describes the following statistical methods; Fisher's Exact Test, Breslow-Day test,
-and Mantel-Haenszel method.
-Section~\ref{sec:app} applies the methods to data from the study, including
-stratafied between ages.
-Section~\ref{sec:discuss} concludes the paper.
+and Mantel-Haenszel method. Section~\ref{sec:app} applies the methods to data 
+from the study, including stratafied between ages. Section~\ref{sec:discuss} 
+concludes the paper.
 
@@
 
+\begin{minipage}{\textwidth}
 2x2 Contingency Table for all patients:
@@
 
+\end{minipage}
+
 \section{Methods}
 \label{sec:methods}
+
+To test the association of breast cancer and Hepatitis C seropositivity, one can use
+the chi-square or Fisher's Exact test, depending on the
+conditions from the sample size \citep{warner2013testing}. Fisher's
+exact test is useful for when the normality assumption is violated 
+and the expected values of the 2x2 table are too small. The test uses 
+the hypergeometric distribution to test if the probabilities are
+the same between the two groups. Thus, we can determine if there is 
+more of a risk of breast cancer for those with seropositive Hep C.
+In the data section, the data was summarized into 2x2 contingency tables.
+The generalzied table is shown in Figure~\ref{fig:table}.
+The first step is calculate the probability of the original table occuring,
+using the hypergeometric pdf. Figure~\ref{fig:formula} shows the formula used.
+
+Based on the alternative hypothesis, you then calculate the probability of 
+all more extreme tables based on the a value. In this paper, p1 is the
+probability of having breast cancer given that the patient is seropositive
+and p2 is the probability of having breat cancer given that the patient
+is seronegative. Then, we want to determine if there is an association,
+specifically if the risk of having breast cancer is higher for those who
+are seropositive. The alternative hypothesis is that p1 is greater than p2-
+which will be tested in the application section.
 
@@
 
-To test the association of breast cancer and Hepatitis C seropositivity, one can use
-the chi-square or Fisher's Exact test, depending on the
-conditions from the sample size \citep{warner2013testing}. Fisher's
-exact test is useful for when the normality assumption is violated 
-and the expected values of the 2x2 table are too small. The test uses 
-the hypergeometric distribution to test if the probabilities are
-the same between the two groups. Thus, we can determine if there is 
-more of a risk of breast cancer for those with seropositive Hep C.
-In the data section, the data was summarized into 2x2 contingency tables.
-The generalzied table is shown in Figure~\ref{fig:table}.
-The first step is calculate the probability of the original table occuring,
-using the hypergeometric pdf. Figure~\ref{fig:formula} shows the formula used.
-
-Based on the alternative hypothesis, you then calculate the probability of 
-all more extreme tables based on the a value. In this paper, p1 is the
-probability of having breast cancer given that the patient is seropositive
-and p2 is the probability of having breat cancer given that the patient
-is seronegative. Then, we want to determine if there is an association,
-specifically if the risk of having breast cancer is higher for those who
-are seropositive. The alternative hypothesis is that p1 is greater than p2-
-which will be tested in the application section.
-
 After calculating the crude estimate, a Breslow-Day test will test for 
@@
 \label{sec:app}
--
+Fisher's exact test for the pooled data of all patients tested 
+\[
+H_{0}:p_{1}=p_{2}, H_{a}:p_{1}>p_{2}
+\]
+at a 0.05 level of confidence.
+
+The test resulted in a p-value of 0.0027, which is less than 
+alpha = 0.05. Thus, the null hypothesis is rejected and there 
+is evidence suggesting patients who are seropositive have a
+higher breast cancer rate than those who are seronegative.
+
+Next, the Breslow Day test checks for homogeneity between the 
+stratified ages. 
+\[
+H_{0}:OR_{1}=OR_{2}, H_{a}:OR_{1}\neq{OR_{2}}
+\]
+at a 0.01 level of confidence.
+
+The test resulted in a p-value of 0.0133, which is greater than
+the alpha value. Thus, we can conclude the strata have similar
+odds ratios and proceed with the Mantel-Haenszel procedure.
+
+The Mantel-Haenszel test produced a common odds ratio of 1.6847 and 
+a 95 percent confidence interval of (0.9283, 3.0574). The interval
+contains 1 so after controlling for age, the association is not supported.
+
+However, the individual odds ratios for age groups are worth noting. For 
+the older group (45 and older) the odds ratio estimate and interval are 
+1.0290 and (0.5197, 2.0374). The odds ratio estimate and interval for the 
+younger group (less than 45) are 7.0318 and (1.5828, 31.2399). Therefore,
+the association between seropositivity and breast cancer is much stronger
+for females less than 45 years.
 
@@
 \label{sec:discuss}
-
--
+Based on the
 

### 2022-11-15 manuscript/manuscript.tex
equations

@@
 
-Recently on October 6th, Egypt and Qatar agreed to collaborate in the health sector and use each 
-other's expertise. The health ministers specifically mentioned research 
+Recently on October 6th, Egypt and Qatar agreed to collaborate in the health sector and 
+use each other's expertise. The health ministers specifically mentioned research 
 in Hepatitis C and breast cancer as an area of interest \citep{arham2022egypt}. 
@@
 
+\vspace{1cm}
+
 \end{minipage}
@@
 The first step is calculate the probability of the original table occuring,
-using the hypergeometric pdf. Figure~\ref{fig:formula} shows the formula used.
+using the hypergeometric pdf:
+\begin{equation}
+P_a=[\frac{(a+b+c+d)a!b!c!d!}{(a+c)!(b+d)!(a+b)!(c+d)!}]^-1
+\end{equation}
 
@@
   \centering
-  \includegraphics[width=8cm]{formula.png}
-  \caption{Hypergeometric pmf}
-  \label{fig:formula}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
   \includegraphics[width=12cm]{2x2 stratified table.png}
@@
 
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=8cm]{breslow day test stat.png}
-  \caption{Breslow Day Test Statistic}
-  \label{fig:BD}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=8cm]{MH Test Stat.png}
-  \caption{Mantel-Haenszel Test Statistic}
-  \label{fig:MH}
-\end{figure}
-
 After calculating the crude estimate, a Breslow-Day test will test for 
@@
 form of stratified 2x2 contingency tables is shown in Figure~\ref{fig:strat}.
-The Breslow-Day test statistic is shown in Figure~\ref{fig:BD}, which will
-be computed using SAS.
+The Breslow-Day test statistic will be computed using SAS with the formula:
+\begin{equation}
+  \chi_{BD}^2=\displaystyle\sum\limits_{i=0}^s\frac{[A_i-E(A_i|\hat{OR}_{M-H})]^2}{Var(A_i|\hat{OR}_{M-H})}
+\end{equation}
 
@@
 is an association between seropositivity and breast cancer while controlling 
-for age. The Mantel-Haenszel test statistic is shown in Figure~\ref{fig:MH}
-where the expected value of A is 
+for age. The Mantel-Haenszel test statistic is:
 \begin{equation}
+  \chi_{M-H}^2=\frac{(|\sum\limits_{i=0}^s A_i - \sum\limits_{i=0}^sE(A_i)|-0.5)^2}
+{\sum\limits_{i=0}^s V(A_i)}
+\end{equation}
+
+\vspace{1cm}
+
+The expected value and variance of A for the ith strata is 
+\[
   E(A_{i})=\frac{M_{i1}R_{1i}}{N_{i}} 
-\end{equation}
-and the variance of A is 
-\begin{equation}
+\]
+\[
   V(A_{i})=\frac{R_{1i}R_{0i}M_{1i}M_{0i}}{N_i^2(N_{i}-1)}. 
-\end{equation}
+\]
 
@@
 \label{sec:discuss}
-Based on the
+Based on the analysis, it is evident that for women under the age of 45,
+seropositivity and breast cancer are strongly associated. As being HCV 
+positive can complicate treatment of cancer, this is critical information.
+In Egypt, breast cancer remains the most common form or cancer and high 
+levels of hepatitus C continue. This study was retrospective so analysis 
+was limited to observing odds ratios and the sample size was quite small.
+Thus, future studies should aim to be prospective cohort studies so 
+researchers can observe how seropisitivity and breast cancer interact 
+over time. 
+Additionally, age is just one factor that can affect the associaiton 
+between hepatitus C and breast cancer. Future studies should dive 
+deeper into more factors such as weight, reproductive history, 
+and alcohol consumption. Addiitonally, future studies can explore how 
+seropositivity affects tumor size, disease agression, and more. As 
+breast cancer is so prevalent in Egypt, further understanding the 
+risk factors is becoming even more importnant.
 

### 2022-11-15 manuscript/manuscript.tex
abstract
refs

@@
 \begin{abstract}
-In Egypt Hepatitus C virus infection is a common problem that often impedes treatment
-of Breast Cancer in female patients. While previous work has analyze an associaiton 
+In Egypt, Hepatitus C virus infection is a common problem that often impedes treatment
+of breast cancer in female patients. While previous work has analyze an associaiton 
 between HCV seropositivity and breast cancer diagnosis, this paper will focus on the 
@@
 breast cancer is so prevalent in Egypt, further understanding the 
-risk factors is becoming even more importnant.
+risk factors is becoming even more important.
+
+\vspace{4cm}
 

### 2022-12-06 manuscript/manuscript.tex
clean
added reference

@@
 \usepackage{array}
-
-\usepackage{lipsum}
+\usepackage{caption}
+\usepackage{setspace}
 \usepackage[colorlinks=true, citecolor=blue]{hyperref}
@@
 
+\doublespacing
 \begin{document}
@@
 
-\begin{minipage}{\textwidth}
-2x2 Contingency Table for all patients:
-
-\begin{tabular}{ | m{4cm} | m{4cm}| m{4cm} | m{2cm} | }
-  \hline
+\begin{center}
+  \captionof{table}{2x2 Contingency Table for all patients}
+\label{tab:all}
+\begin{tabular}{rrrr}
+  \toprule
   & Breast Cancer & No Cancer Diagnosis & Total\\ 
-  \hline
+  \midrule
   HCV Seropositive & 88 & 15 & 103 \\ 
-  \hline
   HCV Seronegative & 317 & 130 & 447 \\ 
-  \hline
+  \midrule
   Total & 405 & 145 & 550 \\ 
-  \hline
+  \bottomrule
 \end{tabular}
+\end{center}
 
@@
 
-2x2 Contingency Table for pateints younger than 45:
-
-\begin{tabular}{ | m{4cm} | m{4cm}| m{4cm} | m{2cm} | }
-  \hline
-    & Breast Cancer & No Cancer Diagnosis & Total\\ 
-  \hline
+\begin{center}
+  \captionof{table}{2x2 Contingency Table for pateints younger than 45}
+\label{tab:younger}
+\begin{tabular}{rrrr}
+  \toprule
+  & Breast Cancer & No Cancer Diagnosos & Total\\
+  \midrule
   HCV Seropositive & 17 & 2 & 19 \\ 
-  \hline
   HCV Seronegative & 110 & 91 & 201 \\ 
-  \hline
+  \midrule
   Total & 127 & 93 & 220 \\ 
-  \hline
+  \bottomrule
 \end{tabular}
+\end{center}
 
@@
 
-2x2 Contingency Table for patients older than 45:
-
-\begin{tabular}{ | m{4cm} | m{4cm}| m{4cm} | m{2cm} | }
-  \hline
+\begin{center}
+  \captionof{table}{2x2 Contingency Table for pateints older than 45}
+\label{tab:older}
+\begin{tabular}{rrrr}
+  \toprule
   & Breast Cancer & No Cancer Diagnosos & Total\\
-  \hline
+  \midrule
   HCV Seropositive & 71 & 13 & 84 \\ 
-  \hline
   HCV Seronegative & 207 & 39 & 246 \\
-  \hline
+  \midrule 
   Total & 278 & 52 & 330 \\ 
-  \hline
+  \bottomrule
 \end{tabular}
+\end{center}
 
 \vspace{1cm}
-
-\end{minipage}
 
@@
 over time.
+
 Additionally, age is just one factor that can affect the associaiton 
@@
 
-\vspace{4cm}
+\pagebreak
 

### 2022-12-06 manuscript/manuscript.tex
fixed equation

@@
 
-This paper will explore the risk factors associated with breast 
-cancer in women. Breast cancer is extremely prevalent and researchers 
-are constantly trying to determine risk factors to identify women for preventative exams.
-There are many studies attempting to determine if there is an association 
-between certain risk factors and breast cancer including chronic hepatitis 
-C infection \citep{Larrey2010is} and hepatitis B \citep{vishnu2016does}.
+Breast cancer is the world's most prevalent cancer and occurs in 
+every country in women at any age after puberty. Therefore,
+it's extremely important to determine certain risk factors 
+that can help detect breast cancer early and save lives. Research 
+is constantly being performed to identify risk factors from lifestyle
+factors to genetics \citep{sun2017risk}. Family history is shown to 
+be a strong predictor for women developing breast cancer.
 
-Specifically, this paper will examine if there is an association between 
-testing positive for hepatitis C virus and breast cancer while controlling 
-for age in Egyptian populations. Both Hepatitis C and breast 
-cancer are extremely prevalent in Egypt \citep{Hussein2021high}.
-Additionally, research has found that women who are seropositive for 
-HCV have more agressive forms of breast cancer. However, there is 
-minimal research concerning the effect of age on the associaiton.
+However, recent research is looking into how certain diseases can be a risk 
+factor for breast cancer or increase the agression of the cancer. 
+Research by the Department of Endocrine and Breast Surgery in China 
+focused on Hepatitis B and it's association with breast cancer and found 
+HBV is potentially affecting estrogen levels, potentially leading 
+to a new way of screening for women \citep{vishnu2016does}. Additionally,
+some work has been done with Hepatitis C seropositivity in France, but 
+the control group was women with other liver diseases \citep{Larrey2010is}.
+Thus, the results can only compare women with certain liver diseases, such as 
+hepatitis B, alcoholic liver disease, and hemochromatosis to 
+women with Hepatitis C.
 
-Recently on October 6th, Egypt and Qatar agreed to collaborate in the health sector and 
-use each other's expertise. The health ministers specifically mentioned research 
+Egypt in particular has the highest prevalence of Hepatitis C, and breast 
+cancer is the most common cancer. Thus, an association between the two 
+would be extremely benficial. So, this paper will examine if there is an 
+association between testing positive for hepatitis C virus and breast cancer 
+diagnosis while controlling for age in Egyptian populations. Age is a knwon 
+and accepted risk factor of breast cancer; older women are more likely to 
+develop tumors \citep{sun2017risk}. Therefore, controlling for age is necessary.
+
+Inconsistency of Hepatitis C prevalence in different regions of Egypt makes 
+it difficult to generalize research to the entire country. This paper will 
+focus on a small region within the country with high 
+prevalence \citep{Hussein2021high} and make conclusions relevent to a specific 
+subgroup.
+
+Recently on October 6th of 2022, Egyptian Minister of Health Abdel-Ghaffar and 
+Qatari Minister of Health Hanan Al-Kuwari met in Doha and agreed to use each 
+other's expertise in the health field. The health ministers specifically mentioned research 
 in Hepatitis C and breast cancer as an area of interest \citep{arham2022egypt}. 
 This meeting emphasizes the importance of diving into Hepatitus C Virus 
-and it's association with breast cancer. There have been conflicting
-foundings so studies should indenify additional variables that could 
-contribute to better understanding the relationship. For that reason,
-this paper is focusing on controlling for age of female patients.
+and it's association with breast cancer. The Egyptian government has defined 
+breast cancer as an area of concern and desires to conduct research within their 
+population, which is very minimal at the moment.
 
@@
 The data used in this paper is from a 2020 retrospective case-control 
-study based on Egyptian female populations \citep{2020association},
-sponsered by Mansoura University in Egypt.
+study based on Egyptian female populations \citep{hussein2020association},
+sponsered by Mansoura University in Egypt. The study was conducted with
+several goals. The main goals we are interested in are 1. to test if seropositivity
+is associated with breat cancer diagnosis in Egyptian population and 
+2. to test if HCV-positive patients harbour more agressive breast tumors 
+than HCV-seronegative patients.
 
 The study group consists of 405 patients treated at the Oncology Center 
-- Mansoura University in the past 10 years. In order to be included, 
+- Mansoura University in the past 10 years. The data was retrieved from
+the hosipital filing system. In order to be included, the patients'
 invasive breast cancer must be biopsy-proven. Patients with unknown 
 viral marker status, multiple cancer diagnoses and virus-unrelated 
-hepatic pathology were all excluded.
+hepatic pathology were all excluded. Additionally, the study measured
+two outcome measures. The primary measure was the prevalence of 
+HCV seropisitivity, which is defined as being Seropositive for the duration
+of the study, an average of 6 months. The secondary outcome measure was
+the number of disease related events related to breast cancer diagnosis. 
+Disease-free survival was calculated from the time of diagnosis to the
+last date of follow up for the study.
 
@@
 females from the same geographic distribution, all with no previous 
-cancer diagnosis. In both groups, all patients are above the age of 
-18. For this paper, patients are stratified based on age- older patients 
+cancer diagnosis. The group consists of healthy volunteers or hosipital
+patients with no cancer diagnosis.
+
+In both groups, all patients are above the age of 
+18. The ratio of study-to-control was intended to be 1:3.
+For this paper, patients are stratified based on age- older patients 
 are considered 45 years or above and younger patients are below 45 years. 
-The data is summarized in the following 2x2 contingency tables.
+The data is summarized in Table~\ref{tab:all}.
 
-\vspace{1cm}
-
+\begin{table}[!h]
   \begin{center}
@@
 \end{center}
+\end{table}
 
-\vspace{1cm}
-
+\begin{table}[!h]
+  \begin{doublespace}
+    Of the 550 women who were involved in the study, 220 were below 
+the age of 45 and 330 were of age 45 or above. Table~\ref{tab:younger} 
+and Table~\ref{tab:older} show the break down of seropositivity and 
+seronegativity for the stratified age groups.
+  \end{doublespace}
   \begin{center}
@@
 \end{center}
+\end{table}
 
-\vspace{1cm}
-
+\begin{table}[!htb]
 \begin{center}
-  \captionof{table}{2x2 Contingency Table for pateints older than 45}
+  \captionof{table}{2x2 Contingency Table for pateints 45 and older}
 \label{tab:older}
@@
 \end{center}
+\end{table}
 

### 2022-12-06 manuscript/manuscript.tex
fix discussion

@@
 more of a risk of breast cancer for those with seropositive Hep C.
+
+The assumptions of Fisher's Exact Test are that all margins of the table 
+are fixed. The total number of subjects with and without the risk factor,
+(A + C) and (B + D) must be fixed. The total number of subjects with and 
+without the event (A + B) and (C + D) must also be fixed. This is 
+equivalent to conditioning on the marginal values.
+
 In the data section, the data was summarized into 2x2 contingency tables.
@@
 The first step is calculate the probability of the original table occuring,
-using the hypergeometric pdf:
+using the hypergeometric probablity mass function:
 \begin{equation}
@@
 \end{equation}
+The hypergeometric distribution is a discrete distribution, so we use the 
+probability mass function for calculations where A is the random variable 
+representing the count in the (1,1) cell.
 
-Based on the alternative hypothesis, you then calculate the probability of 
-all more extreme tables based on the a value. In this paper, p1 is the
+After finding the probability of the original table, you then calculate the probability of 
+all more extreme tables based on the a value. Fisher's exact test is often 
+a one-sided test based on the research being conducted. In this paper, p1 is the
 probability of having breast cancer given that the patient is seropositive
@@
 
-After calculating the crude estimate, a Breslow-Day test will test for 
-homogeneity of odds ratios between the age stratified data. The generalized
+After calculating the crude estimate without age stratfied, 
+a Breslow-Day test will test for homogeneity of odds ratios between 
+the age stratified data, younger than 45 and age 45 or older. The generalized
 form of stratified 2x2 contingency tables is shown in Figure~\ref{fig:strat}.
+The risk factor is in the rows while the event of interest is in the columns.
+Each strata forms its own table that is used for calculations. 
 The Breslow-Day test statistic will be computed using SAS with the formula:
+\vspace{0.5cm}
 \begin{equation}
@@
 \end{equation}
+\vspace{0.5cm}
 
@@
 is an association between seropositivity and breast cancer while controlling 
-for age. The Mantel-Haenszel test statistic is:
+for age. The Mantel-Haenszel test can only be conducted if the homogeneity of 
+odds ratios is not rejected. The Mantel-Haenszel test statistic is:
+\vspace{0.5cm}
+
 \begin{equation}
@@
 
-\vspace{1cm}
+\vspace{0.5cm}
 
@@
 
+This procedure only focuses on odds ratios so it can be used for prospective, 
+retrospective, and cross-sectional studies. Additionally, it focuses on the (1,1) 
+cell on the table just like Fisher's Exact test. It should be noted that the test 
+statistic includes a continuity correction while SAS computes the test statistic 
+without a continuity correction.
+
 \section{Application}
 \label{sec:app}
+As stated in the methods section, we will begin with Fisher's Exact test to 
+determine the relationship between HCV seropositivity and breast cancer without 
+controlling for age. Then, we will conduct a Breslow-Day test to test for 
+homogeneity of odds ratios between the age stratified data. Finally, we will 
+perform a Mantel-Haenszel test to compare the strata.
+
 Fisher's exact test for the pooled data of all patients tested 
@@
 is evidence suggesting patients who are seropositive have a
-higher breast cancer rate than those who are seronegative.
+higher breast cancer rate than those who are seronegative 
+without controlling for age.
 
@@
 \]
-at a 0.01 level of confidence.
+at a 0.01 level of confidence. Where OR 1 is the odds ratio of 
+women who did and did not develop breast cancer with seropositivity 
+for women younger than 45 and OR2 is the odds ratio of women who 
+did and did not develop breast cancer with seropositivity for women 
+45 years and older.
 
 The test resulted in a p-value of 0.0133, which is greater than
-the alpha value. Thus, we can conclude the strata have similar
+the alpha value of 0.05. Thus, we fail to reject the null hypothesis 
+and conclude there is not ennough evidence to suggest the strata have different
 odds ratios and proceed with the Mantel-Haenszel procedure.
@@
 contains 1 so after controlling for age, the association is not supported.
+Addtionally, we will test the following hypothesis using the Mantel-Haenszel 
+test statistic:
+\[
+H_{0}:OR_{common}=1, H_{a}:OR_{common}\neq{OR_{1}}
+\]
+
+The calculated p-value is 0.0773. Therefore, the fail to reject the null 
+hypothesis and there is not enough evidence that there is an association 
+between HCV seropositivity and breast cancer diagnosis after controlling for 
+age.
 
@@
 In Egypt, breast cancer remains the most common form or cancer and high 
-levels of hepatitus C continue. This study was retrospective so analysis 
-was limited to observing odds ratios and the sample size was quite small.
+levels of hepatitus C continue.
+
+There are several limitations to the study that call into question the 
+validity of the results. The small sample size is a result of lack 
+of available data. Therefore, it is hard to find a meaningful 
+association. The study was retrospective, which limited analysis to 
+the odds ratio and not risk difference or relative risk. The method 
+of data collection of the control group is also not ideal. Using historical 
+data can cause issues as direct populations are not being compared. 
 Thus, future studies should aim to be prospective cohort studies so 
-researchers can observe how seropisitivity and breast cancer interact 
+researchers can observe how seropositivity and breast cancer interact 
 over time.
@@
 breast cancer is so prevalent in Egypt, further understanding the 
-risk factors is becoming even more important.
+risk factors is becoming even more important. The collaboartion between Egypt 
+and Qatar is very promising for emerging research in the health sector. 
+With resources and knowledge from Qatar, it is hopeful that Egypt 
+can research further into Hepatitis C and breast cancer for the good 
+of their population.
 

### 2022-12-06 manuscript/manuscript.tex
refs

@@
 
-The rest of the paper is organized into several sections. Section~\ref{sec:data}
+The rest of the paper is organized into several sections that will explain the 
+research question and the methods used to evaluate the data. Section~\ref{sec:data}
 describes the study done in 2020 to test if HCV seropositivity is associated with 
@@
 describes the following statistical methods; Fisher's Exact Test, Breslow-Day test,
-and Mantel-Haenszel method. Section~\ref{sec:app} applies the methods to data 
-from the study, including stratafied between ages. Section~\ref{sec:discuss} 
-concludes the paper.
+and Mantel-Haenszel method, and their respective assumptions. 
+Section~\ref{sec:app} applies the methods to data 
+from the study, including both crude and stratafied between ages. 
+Section~\ref{sec:discuss} concludes the paper with results.
 
@@
   Based on the analysis, it is evident that for women under the age of 45,
-seropositivity and breast cancer are strongly associated. As being HCV 
-positive can complicate treatment of cancer, this is critical information.
-In Egypt, breast cancer remains the most common form or cancer and high 
-levels of hepatitus C continue.
+seropositivity and breast cancer are strongly associated. However, there 
+is not enough to suggest an association for women 45 years and older. 
+As being HCV positive can complicate treatment of cancer or act as 
+an effective risk factor for increase screening for women, this is 
+critical information. More research is necessary to determine how strong 
+the association is or further break down age groups into smaller strata.
 
